---
title: "analaysis old"
output: html_document
---

Panel A (centralized and decentralized)

```{r fig.height=4, fig.width=8}
a <-df %>%
  group_by(yr, name) %>%
  summarise(count = sum(value),
            total_words = sum(total_words)) %>%
  mutate(TF = count/total_words) %>%
  filter(yr >1980 & yr<2021) %>%
  filter(name == "centralized" | name == "decentralized") %>%
  ggplot(aes(x = yr, y = TF*1000, color = name , type = name)) +
  geom_line() + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  expand_limits(x = c(1980, 2025)) +
  geom_dl(aes(label = name), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5)) 

```

# 
```{r fig.width = 4, fig.height=4}
b <- df %>%
    filter(agroforestry>quantile(df$agroforestry,0.25)) %>%
  group_by(yr, name) %>%
  summarise(count = sum(value),
            total_words = sum(total_words)) %>%
  mutate(TF = count/total_words) %>%
  filter(yr >1980 & yr<2021) %>%
  filter(name != "centralized" & name != "decentralized") %>%
  filter(name == "agreements" |  
           name == "policy" |
             name == "spatial" | 
              name == "institutions") %>%
  ggplot(aes(x = yr, y = TF*1000, color = name , type = name)) +
  geom_line() + 
  theme_classic() +
    geom_vline(xintercept = 2007, colour="grey", linetype = "dashed") +
    geom_text(aes(x=2005.5, label="IPCC", y=10), colour="grey", angle= 90, text=element_text(size=4)) +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  expand_limits(x = c(1980, 2025)) +
  geom_dl(aes(label = name), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5)) 

```


```{r fig.width= 4, fig.height=4}
c <- df %>%
    filter(agroforestry>quantile(df$agroforestry,0.25)) %>%
  group_by(yr, name) %>%
  summarise(count = sum(value),
            total_words = sum(total_words)) %>%
  mutate(TF = count/total_words) %>%
  filter(yr >1980 & yr<2021) %>%
  filter(name != "centralized" & name != "decentralized") %>%
  filter(name != "agreements" &  
           name != "policy" &
             name != "spatial" & 
              name != "institutions") %>%
  ggplot(aes(x = yr, y = TF*1000, color = name , type = name)) +
  geom_line() + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  expand_limits(x = c(1980, 2025)) +
  geom_dl(aes(label = name), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5)) 

```

```{r fig.width=8, fig.height=6, dpi = 300}
ggarrange(a,                                                 # First row with scatter plot
          ggarrange(b, c, ncol = 2, labels = c("B", "C")), # Second row with box and dot plots
          nrow = 2, 
          labels = "A"  )                                      # Labels of the scatter plot
```


##


```{r dpi = 300}
df %>%
  filter(agroforestry>quantile(df$agroforestry,0.25)) %>%
  filter(name == "centralized" | name == "decentralized") %>%
  pivot_wider(id_cols = c(yr,ID, total_words), names_from = name, values_from = TF) %>%
  mutate(ratio = centralized/(decentralized+centralized))%>%
  mutate(decade = ifelse(yr>1980 & yr<1990, "80s", 
                         ifelse(yr>1989 & yr<2000, "90s",
                                ifelse(yr>1999 & yr<2010, "00s",
                                      ifelse(yr>2009 & yr<2020, "10s", "20s"))))) %>%
  filter(yr>1980 & yr<2020) %>%
  drop_na() %>%
  #mutate(perc_words = total_words/yr_words) %>%
  #mutate(ratio_weight = ratio * perc_words) %>%
  #group_by(yr) %>%
  #summarise(ratio = mean(ratio)) %>%
  ggplot(aes(x = ratio, fill = decade)) + geom_histogram() +
  facet_grid(rows = vars(decade))
```




```{r}
coord <- df %>%
  filter(name != "centralized" & name != "decentralized") %>%
  pivot_wider(id_cols = c(yr,ID, total_words), names_from = name, values_from = TF) %>%
  select(agreements:methods) 

```

```{r fig.height=6, fig.width=8, dpi = 300}
cormat <-cor(coord)
library(reshape2)
melted_cormat <- melt(cormat)

ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile() + theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

```{r}
# install if necessary
# install.packages('igraph')
library(igraph)
 
my_adj_list <- melted_cormat %>% filter(value > 0.95)

# create igraph S3 object
net <- graph.data.frame(melted_cormat, directed = FALSE)
 
# store original margins
orig_mar <- par()$mar
 
# set new margins to limit whitespace in plot
par(mar=rep(.1, 4))

# not much difference in the edge width given the values
# but I included it for reference's sake
plot(net, layout = layout_components(net), edge.width = E(net)$weight)
plot(net, layout = layout_components(net), edge.width = E(net)$weight, vertex.shape="none")
```




```{r}
normalize2 <- function(x, na.rm = T) (x  / max(x, na.rm = T))
df_filter <- df %>%
  filter(agroforestry>quantile(df$agroforestry,0.25)) %>%
  pivot_wider(id_cols = c(ID, yr),names_from = name, values_from = TF) 

df_filter%>% 
  mutate_at('centralized', normalize2) %>%
  mutate_at('decentralized', normalize2) %>%
  filter(centralized < 1) %>%
  ggplot(aes(x=centralized, y = decentralized, col = yr)) +geom_point()
```



  
agroforestry %>%
  ggplot(aes(x = yr, y = agroforestry_1)) +
  geom_line()

agroforestry %>% select(yr, transition_1, adoption_1) %>%
  pivot_longer(-yr) %>%
  ggplot(aes(x = yr, y = value, col = name)) +
  geom_line()


agroforestry %>% filter(yr>1980) %>%
  select(yr, agroforestry_1, climate_1, carbon_1, IPCC_1, 
          mitigation_1, NDC_1, NCS_1) %>%
  pivot_longer(-c(yr, agroforestry_1)) %>%
  ggplot(aes(x = yr, y = value/agroforestry_1, col = name)) +
  geom_line()


agroforestry %>% filter(yr>1980) %>%
  select(yr, agroforestry_1, adaptation_1 , resilience_1,
         farmers_1, farm_1) %>%
  pivot_longer(-c(yr, agroforestry_1)) %>%
  ggplot(aes(x = yr, y = value/agroforestry_1, col = name)) +
  geom_line()

agroforestry %>% filter(yr>1980) %>%
  select(yr,agroforestry_1, local_1, national_1 , international_1,
         global_1, `multi-scalar_1`) %>%
  pivot_longer(-c(yr, agroforestry_1)) %>%
  ggplot(aes(x = yr, y = value/agroforestry_1, col = name)) +
  geom_line()

agroforestry %>% filter(yr>1980) %>%
  select(yr,agroforestry_1, feminist_1, postcolonial_1, social_1, gender_1, indigenous_1, SES_1) %>%
  pivot_longer(-c(yr, agroforestry_1)) %>%
  ggplot(aes(x = yr, y = value/agroforestry_1, col = name)) +
  geom_line()
```